Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains

### 2016-06-23 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex

		H_{eq} = \frac{1}{t_{total}}\sum_{i=1}^N\int_{t_i}^{t_i+\tau}\mathrm{d}t~h_i(t) = \frac{\tau}{2t_{total}}\sum_{i=1}^NH_i,

@@

	where $t_{total}$ is the total simulation time. Note that if $H_i=H_0$ for all $i$, the uniform heating rate $H_0=2t_{total}H_{eq}/N\tau$. Thus, for $L=40$ Mm, $A=10^{14}$ cm$^2$, the total amount of energy injected into the loop by one heating event for a loop heated by $N=20$ nanoflares in $t_{tot}=8\times10^4$ s is $\varepsilon=LAt_{total}H_{eq}/N\approx7.2\times10^{24}$ erg, consistent with the energy budget of the Parker nanoflare model. 

@@

	\par Determining the heating frequency in AR cores will help to place constraints on the source(s) of heat in the corona. We define the heating frequency in terms of the waiting time, $t_N$, between successive heating events. Following \citet{cargill_active_2014}, the range of waiting times is $250\le t_N\le5000$ s in increments of 250 s, for a total of 20 different possible heating frequencies. Additionally, $t_N$ can be written as $t_N=(t_{total}-N\tau)/N$, where we fix $T=8\times10^4$ s and $\tau=200$ s. Note that because $t_{total}$ and $\tau$ are fixed, as $t_N$ increases, $N$ decreases. Correspondingly, $\varepsilon_i$, the energy injected per event, increases according to \autoref{eq:heating_rate_constraint} such that the total energy injected per run is constant, regardless of $t_N$.

@@

	\par We now show the results of our loop simulations for each point in our multi-dimensional parameter space: species heated (single-fluid, electron or ion), power-law index ($\alpha$), heating frequency ($t_N$), and waiting-time/event energy relationship ($\beta$). All results were processed using the IPython system for interactive scientific computing in Python \citep{perez_ipython:_2007} as well as the NumPy and Scipy numerical and scientific Python libraries \citep{van_der_walt_numpy_2011}. All results were visualized using the matplotlib graphics library \citep{hunter_matplotlib:_2007}.
	\par In order to compactly summarize all of the data in each run of our model, we calculate the resulting emission measure distribution using the familiar expression $\mathrm{EM}=n^2(2L)$, where $L$ is the loop half-length. We consider a temperature range of $4.0\le\log{T}\le8.5$ with bin sizes of $\Delta\log{T}=0.01$. At each iteration $i$, the coronal temperature range $[T_0,T_a]$ is calculated from $\bar{T}_e$. For each bin that falls within $[T_0,T_a]$, $\bar{n}_i^2(2L)$ is added to that bin, where $\bar{n}_i$ is the spatially-averaged number density at time $t_i$. The emission measure in each bin is then averaged over the entire simulation period. When measured observationally, $\mathrm{EM}(T)$ is a line-of-sight quantity. Assuming an aspect ratio (i.e. ratio of loop length to loop width) of 10, we apply a correction factor 1/10 to all calculated $\mathrm{EM}$ curves. Furthermore, each emission measure distribution we also compute the corresponding effective emission measure distribution, $\mathrm{EM}(T_{eff})$, using $T_{eff}$, the effective temperature calculated by including effects due to NEI.
	\par As noted in \autoref{subsec:heating_stats}, for each heating frequency $t_N$, we compute $N_R$ runs such that there are $N_R$ $\mathrm{EM}(T)$ distributions for each $t_N$. Thus, the $\mathrm{EM}(T)$ that we show for each $t_N$ is the average computed over all $N_R$ of these emission measure distributions. 

@@

@@

		\caption{Emission measure distributions for varying waiting-times, $t_N$ in the case where only the electrons are heated. The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green). The dotted lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution.}

@@

	\par First, we look at the resulting emission measure distributions for the case in which only the electrons are heated. \autoref{fig:el_em} shows $\mathrm{EM}(T)$ for six different values of $t_N$ and three different types of heating functions: uniform heating events, events chosen from a power-law distribution of index $\alpha=-2.5$, and events chosen from a power-law distribution of index $\alpha=-2.5$ where the time between successive events depends on the heating rate of the preceding event. The dotted lines in each frame show the corresponding emission measure distribution constructed from $T_{eff}$, $\mathrm{EM}(T_{eff})$.
	\par As $t_N$ increases, $\mathrm{EM}$ is allowed to extend to both lower and 

@@

		\caption{Same as \autoref{fig:el_em}, but for the case where only the ions are heated.}

@@

	\par \autoref{fig:el_em} and \autoref{fig:ion_em} show the results of our emission measure study for the two distinct cases where only the electrons are heated and only the ions are heated with $\alpha=-2.5,\beta=1$ for a loop half-length of $40$ Mm, consistent with \citetalias{barnes_inference_2016}. The panels on the left show the mean $\mathrm{EM}$ for all $t_N$, where the average is taken over all $N_{R}$ runs. There is an artifical spacing of $\Delta\log{\mathrm{EM}}=0.2$ between each curve so that they can be easily distinguished from each other. The blue (red) lines indicate the cool (hot) power-law fits, where the slopes of the lines are the averages taken over all $N_{R}$ runs. We note that the $\mathrm{EM}$, for all $t_N$, peaks at approximately 4 MK ($10^{6.6}$ K), consistent with the constraints laid out in \autoref{subsec:params}. The top right panels show these average slope values as a function of $t_N$. The error bars indicate one standard deviation as calculated from the distribution of all $N_{R}$ runs.

@@

	\par Lastly, the bottom right panels show the first derivative as a function of temperature, $d\log{\mathrm{EM}}/d\log{T}$, computed using central differences. The color scheme and line styles correspond to the emission mesure curves in the left panel. As in \citetalias{barnes_inference_2016}, we compute the derivative in an effort to better assess at what temperatures the emission measure is not well described by a power-law.

@@

@@

@@

@@

@@

@@

>>>>

		H_{eq} = \frac{1}{t_{total}}\sum_{i=1}^N\int_{t_i}^{t_i+\tau}\mathrm{d}t~Q(t) = \frac{\tau}{2t_{total}}\sum_{i=1}^NH_i,

@@

	where $t_{total}$ is the total simulation time. Note that if $H_i=H_0$ for all $i$, the heating rate for each event is $H_i=H_0=2t_{total}H_{eq}/N\tau$. Thus, for $L=40$ Mm, $A=10^{14}$ cm$^2$, the average energy per event for a loop heated by $N=20$ nanoflares in $t_{total}=8\times10^4$ s is $\varepsilon=LAt_{total}H_{eq}/N\approx5.8\times10^{24}$ erg, consistent with the energy budget of the Parker nanoflare model. 

@@

	\par We define the heating frequency in terms of the waiting time, $t_N$, between successive heating events. Following \citet{cargill_active_2014}, the range of waiting times is $250\le t_N\le5000$ s in increments of 250 s, for a total of 20 different possible heating frequencies. Additionally, $t_N$ can be written as $t_N=(t_{total}-N\tau)/N$, where we fix $t_{total}=8\times10^4$ s and $\tau=200$ s. Note that because $t_{total}$ and $\tau$ are fixed, as $t_N$ increases, $N$ decreases. Correspondingly, $\varepsilon_i=LA\tau H_i/2$, the energy injected per event, increases according to \autoref{eq:heating_rate_constraint} such that the total energy injected per run is constant, independent of $t_N$.

@@

	\par We now show the results of our loop simulations for each point in our multi-dimensional parameter space: species heated (single-fluid, electron or ion), power-law index ($\alpha$), heating frequency ($t_N$), and waiting-time/event energy relationship ($\beta$). In each 0D hydrodynamic simulation, a loop of half-length $L=40$ Mm is heated by $N$ triangular events of duration $\tau=200$ s and peak heating rate $H_i$ for a duration of $t_{total}=8\times10^4$ s. The average interval between subsequent events is $t_N$ (in the uniform and power-law case, $t_N,i=t_N$ exactly for all $i$). We focus primarily on the emission measure distribution, $\mathrm{EM}(T)$, and observables typically calculated from $\mathrm{EM}(T)$. In all cases, the coronal emission measure is calculated according to the method outlined in section 3 of \citetalias{barnes_inference_2016}. The corresponding NEI results, $\mathrm{EM}(T_{eff})$, are calculated similarly, but using $T_{eff}$ (see \autoref{subsec:nei}) instead of $T$. All results were processed using the IPython system for interactive scientific computing in Python \citep{perez_ipython:_2007} as well as the NumPy and Scipy numerical and scientific Python libraries \citep{van_der_walt_numpy_2011}. All results were visualized using the matplotlib graphics library \citep{hunter_matplotlib:_2007}.

@@

		\includegraphics[width=2\columnwidth]{figures/em_grid_single_a25.pdf}
		\caption{Emission measure distributions for waiting-times $t_N=250,750,1500,2500,3750,5000$ s in the single-fluid case. The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green). The dotted lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution.}
		\label{fig:single_em}

@@

		\caption{Same as \autoref{fig:single_em}, but for the case where only the electrons are heated.}

@@

@@

		\caption{Same as \autoref{fig:single_em}, but for the case where only the ions are heated.}

@@

	\par In our first set of results, we compare $\mathrm{EM}(T)$ for three different types of heating functions, across six different heating frequencies. \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} show the emission measure distributions in the single-fluid case, electron heating case, and ion heating case, respectively. Each panel in each figure corresponds to a different waiting time ($t_N$) and includes three different types of heating functions: uniform heating events (red), events chosen from a power-law distribution of index $\alpha=-2.5$ (blue), and events chosen from a power-law distribution of index $\alpha=-2.5$ where the time between successive events depends on the heating rate of the preceding event (green). Furthermore, the dashed lines denote the corresponding NEI cases, $\mathrm{EM}(T_{eff})$.

@@

	\par Recall from \autoref{subsec:heating_stats} that for those heating functions which choose peak heating rates from a power-law distribution, for each $t_N$, we run the model $N_R\sim(t_N+200)/8$ times. Thus, for each point in our parameter space, we produce $N_R$ $\mathrm{EM}(T)$ curves. In order to present our results compactly, the panels of \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} each show the average over all $N_R$ curves. In this way, we account for the variations that may occur because of a lack/excess of strong heating events due to limited sampling from the distribution.

@@

	\par We look first at the $\mathrm{EM}(T)$ for the single-fluid case, \autoref{fig:single_em}. Looking at all six panels, we note that as $t_N$ increases, $\mathrm{EM}(T)$ widens towards both cooler and hotter temperatures. $\mathrm{EM}(T)$ extends toward cooler temperatures because as $t_N$ increases and there is more time between successive heating events, the loop is allowed more time to cool both by radiation and enthalpy flux. $\mathrm{EM}(T)$ extends towards hotter temperatures for similar, but more subtle reasons. As $t_N\to0$, we approach the steady heating case in which conductive and radiative cooling exactly balance the heating. As $t_N$ increases and becomes comparable to and greater than a cooling time, the loop beceomes increasingly tenuous at the time of the subsequent heating event, allowing the loop to reach much hotter temperatures as radiative cooling is very inefficient at low densities. In this way, $\mathrm{EM}(T)$ can ``see'' this greater range of temperatures, both hot and cool, provided it is allowed to undergo a typical heating and cooling cycle. The more curtailed this cycle is by continued reheatings, the more narrow $\mathrm{EM}(T)$ will be.

@@

	\par\hl{Describe differences between different heating function types} Looking at the different curves in each panel of \autoref{fig:single_em}, it is important to note that, although all widen as $t_N$, the way each extends higher and lower temperatures is very different. 

@@

	\par\hl{Address electron and ion cases and how they differ from the single-fluid case in the ways discussed above.}

@@

	\par\hl{Describe differences between IEQ and NEI solutions.}
	%%%%%%%%%%%%%

@@

	\par\hl{Mostly discussing differences between power-law and uniform on hot side and scaling/non-scaling on the cool side. Lead into this paragraph from the previous paragraph}

@@

		\includegraphics[width=2\columnwidth]{figures/em_slope_varying_bounds.pdf}
		\caption{\textbf{Left:} EM slope as a function of upper bound on fit interval for both the hot (red) and cool (blue) side of $EM(T)$. \textbf{Right:} Emission measure distribution with overlaid hot and cool fit lines for varying fit intervals.}
